Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-26 paper/paper.tex
revising descriptioin of Malicious traffic

\subsubsection{Malicious traffic.}~For some of the attacks listed on
Table~\ref{table:attacks}, we obtained pcap files directly from
trusted security websites (\eg{},
NetReseC~\cite{pcap-attacks}). Recall that \tname\ takes pcap files on
input. As explained in Section~\ref{sec:minimization}, these files
abstract network messages~\cite{pcap} and can be used to avoid network
traffic during rule synthesis. In addition to these sources, we used
the Nikto2~\cite{nikto} open source security tool to reproduce
attacks. To reproduce the http and tcp attacks listed on
Table~\ref{table:attacks}, we configured an http server (Apache2) in
one machine and ran the security tool in a different
machine. Simultenously, we ran WireShark~\cite{wireshark-net-monitor}
to record the network traffic and Suricata to analyze the traffic. We
configured \suri\ with all rules from the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} and ran Nikto2 with default
parameters, which makes it replay all recorded attacks. After
execution, we inspected the \suri\ log to identify which rules have
been activated and which packets were involved in each
activation. With the packet numbers, it is possible to recover the
corresponding pcap files, using Wireshark, as to ran \tname{} on
them. It is worth noting that some rules are triggered multiple times,
indicating that there are multiple instances of the same attack
encoded in Nikto2. RQ3 evaluates the importance of these variants to
\tname{}'s performance. Finally, Nikto2 only supports tcp and http
attacks.  We used the hping3~\cite{hping3} to reproduce the Ping Scan
icmp attack (see Section~\ref{sec:dos}).  More precisely, we used the
following hping3 command to reproduce that attack: \CodeIn{hping3 -d
  80 -w 512 -S -p 80 --flood --rand-source <IP>}.

>>>>

\subsubsection{Malicious traffic.}~For some of the attacks listed on
Table~\ref{table:attacks}, we obtained pcap files directly from
trusted security websites (\eg{},
NetReseC~\cite{pcap-attacks}). Recall that \tname\ takes pcap files on
input. As explained on Section~\ref{sec:minimization}, these files
abstract network messages~\cite{pcap} and can be used to avoid network
traffic during rule synthesis. In addition to these sources, we used
the Nikto2~\cite{nikto} open source security tool to reproduce
attacks. To reproduce the http and tcp attacks listed on
Table~\ref{table:attacks}, we configured an http server (Apache2) and
ran a security tool to attack that server. Simultenously, we ran
WireShark~\cite{wireshark-net-monitor} to record the network traffic
and Suricata to analyze the traffic. We configured \suri\ with all
rules from the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} and configured Nikto2 with
default parameters, which makes it replay all recorded attacks. After
execution, we inspected the \suri\ log to identify which rules have
been activated and which packets were involved in each
activation. With the packet numbers, it is possible to recover the
corresponding pcap files, using Wireshark, as to ran \tname{} on
them. It is worth noting that some rules are triggered multiple times,
indicating that there are multiple instances of the same attack
encoded in Nikto2\Mar{@Lucas, diga exatamente como vc. obtem as
  variacoes. isto eh que eh importante para a proxima sentenca.}. rq3 evaluates the importance of these variants to
\tname{}'s performance. Finally, Nikto2 only supports tcp and http
attacks.  We used the hping3~\cite{hping3} to reproduce the Ping Scan
icmp attack (see Section~\ref{sec:dos}).  More precisely, we used the
following hping3 command to reproduce that attack: \CodeIn{hping3 -d
  80 -w 512 -S -p 80 --flood --rand-source <IP>}.
